Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-04 ijar-npb-ms.tex
figure with sets of beta cdfs and sets of bebin cmfs, more small improvements in sections 5 and 6

For discussing this reparametrisation, we will drop the super- and subscript $k$ and $t$ for a while.
Instead of $\alpha$ and $\beta$, we consider the parameters $\nz$ and $\yz$, where
\begin{align}
\nz &= \alpha + \beta &
&\text{and} &
\yz &= \frac{\alpha}{\alpha + \beta} \,,
\label{eq:reparam}
\end{align}
or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
The upper index ${}\uz$ is used to identify $\nz$ and $\yz$ as prior parameter values,
in contrast to their posterior values $\nn$ and $\yn$
obtained after observing $n$ failure times, see below.
$\nz$ and $\yz$ are sometimes called \emph{canonical} parameters,
identified from rewriting the density in a canonical form;
see, e.g., \citet[pp.~202 and 272f]{2000:bernardosmith}.
This canonical form gives a joint structure to all conjugate priors in exponential families.

@@

As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
This element-by-element updating may seem ad-hoc, but can be rigorously justified
as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well
\citep[pp.~123f]{2013:diss-gw}; \citep{Troffaes2013a-short}.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

\begin{figure}
\includegraphics[width=\textwidth]{paramsets}
\caption{Prior parameter set $\PktZ = [1,8] \times [0.7,0.8]$ and posterior parameter set $\PktN$
for data $s^k_t/n_k = 12/16$ (left) and $s^k_t/n_k = 0/16$ (right).
For no-conflict data ($s^k_t/n_k \in [\yktzl,\yktzu]$), $\PktN$ has the `spotlight' shape (left);
in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right).}
\label{fig:paramsets}
\end{figure}

@@

In case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl, \yktzu]$),
$\PktN$ has instead the so-called banana shape,
arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
Overall, this results in a wider $\yktn$ interval as compared to the non-conflict case, 
reflecting the extra uncertainty due to prior-data conflict,
thus making more cautious probability statements about $p_t^k$.

\td{Figure with sets of beta cdfs and beta-binom cmfs for conflict and no conflict case.}

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance in a more adequate way,
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
(It is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
E.g., for any $t < \min(\vec{t}^k)$,
we would get $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
Choosing these limits for $\yktz$ means that we are prepared to give trivial bounds for the functioning probability only,
and do not wish to make any commitments about $p^k_t$ a priori.
Compare this to the uniform prior over $[0,1]$, a usual choice of `noninformative' prior,
being a Beta prior with $\alpha^k_t = \beta^k_t = 1$, i.e., $\nktz = 2$, $\yktz = 0.5$.
Taking this for all $t \in {\cal T}$ means that we expect the component reliability function
to be on average 1/2 for all $t$, a very peculiar assumption,
and, in our view, quite incompatible with the notion of prior ignorance.

For an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
as then one of the bounds for $\ykt$ is attained for $\nktzl$.
In a near-noninformative setting, the choice of $\nktzl$ is instead not relevant,
as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Obviously, one cannot have prior-data conflict in case of prior near ignorance.

\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
benavoli zaffalon papers***}

@@

We think it is not advisable to express certainty about expected functioning probabilities
with $\nktz$ bounds that vary strongly over $t$.
%***Better to express certainty of prior guess via $\nktz$ bounds?\\
With (strongly) differing $\nktz$ bounds, monotonicty for $\yktn$ bounds cannot be ensured.
%it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so there is no prior-data conflict),
and furthermore no failures happening in $[t_j, t_{j+1}]$, i.e., $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
\begin{itemize}
\item for $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we get $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$, and
\item for $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we get $\ynl_{k,t_j} < \ynl_{k,t_{j+1}}$.
\end{itemize}
Again, this follows from the weighted average property of $\yktn$;
for constant $\yktz$, the lower $\nktz$ the closer $\yktn$ is to $s^k_t/n_k$.
% one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to have it change with $t$ gradually only.

Generally, the interpretation as pseudocount or prior strength should guide the choice of bounds for $\nktz$; 
low values for $\nktz$ as compared to the test sample size $n_k$
give low weight to the prior expected functioning probability intervals $[\yktzl, \yktzu]$,
and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
in a no-conflict situation, when $\nktzu = n_k$ $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
which means more cautious posterior inferences.
The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
as is clear from Figure~***, the wider the $\nktz$ interval,
the wider $[\yktnl, \yktnu]$ in case of conflict.
So it seems useful to choose $\nktzl = 1$ or $\nktzl = 2$,
while choosing $\nktzu$ with help of the half-width rule as described above.

%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
%to get proper posteriors***
As mentioned in Section~\ref{sec:setsofbetapriors},
it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
this can lead to improper posterior predictive distributions if $l_k=0$ or $l_k=m_k$.
%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
But it is possible to choose values close to $0$ and $1$, respectively,
and due to the linear update step for $\yktn$ (see Eq.~\eqref{eq:nyupdate}),
posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
%***what to do in extreme tail of component distributions?
%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
Likewise, our nonparametric method does not bring unintuitive tail behaviour
as some parametric methods do;
there is no problem in, e.g., assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.

%***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
%as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
While it is possible to set the bounds $\yktzl$ and $\yktzu$ for each $t \in {\cal T}$ individually,
in practice this will be often too time-consuming when ${\cal T}$ forms a dense grid.
%(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Switching to a coarser time grid will waste information from data,
as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
We rather propose to elicit bounds only for a subset of ${\cal T}$,
and to fill up the $t$ grid with the least committal bounds, i.e.,
taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
an likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
A possible elicitation procedure in this vein could be
to start with eliciting $\yktz$ bounds for a few `central' time points $t$,
filling up the grid as described above accordingly,
and then to further refine the obtained bounds if necessary.
%`middle' or `typical' $t$,
%then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,

>>>>

For discussing this reparametrisation, we will drop the super- and subscript $k$ and $t$ for a while.
Instead of $\alpha$ and $\beta$, we consider the parameters $\nz$ and $\yz$, where
\begin{align}
\nz &= \alpha + \beta &
&\text{and} &
\yz &= \frac{\alpha}{\alpha + \beta} \,,
\label{eq:reparam}
\end{align}
or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
The upper index ${}\uz$ is used to identify $\nz$ and $\yz$ as prior parameter values,
in contrast to their posterior values $\nn$ and $\yn$
obtained after observing $n$ failure times, see below.
$\nz$ and $\yz$ are sometimes called \emph{canonical} parameters,
identified from rewriting the density in a canonical form;
see, e.g., \citet[pp.~202 and 272f]{2000:bernardosmith}, or \citet[\S 1.2.3.1]{2013:diss-gw}.
This canonical form gives a joint structure to all conjugate priors in exponential families.

@@

As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
This element-by-element updating may seem ad-hoc, but can be rigorously justified
as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\label{eq:paramsets}
\end{align}
Examples for parameter sets $\PktZ$ and $\PktN$ as in \eqref{eq:paramsets} are depicted in Figure~\ref{fig:paramsets}.
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well
\citep[pp.~123f]{2013:diss-gw}; \citep{Troffaes2013a-short}.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

\begin{figure}
\includegraphics[width=\textwidth]{paramsets}
\caption{Prior parameter set $\PktZ = [1,8] \times [0.7,0.8]$ and posterior parameter set $\PktN$
for data $s^k_t/n_k = 12/16$ (Posterior 1, left) and $s^k_t/n_k = 0/16$ (Posterior 2, right).
For no-conflict data ($s^k_t/n_k \in [\yktzl,\yktzu]$), $\PktN$ has the `spotlight' shape (left);
in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right),
leading to a large degree of imprecision in the $\yktn$ dimension of $\PktN$,
thus reflecting increased uncertainty about the functioning probability $p^k_t$
due to the conflict between prior assumptions and observed data.}
\label{fig:paramsets}
\end{figure}

@@

In case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl, \yktzu]$),
$\PktN$ has instead the so-called banana shape,
arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
Overall, this results in a wider $\yktn$ interval as compared to the no conflict case, 
reflecting the extra uncertainty due to prior-data conflict,
thus making more cautious probability statements about $p_t^k$.

Based on these shapes and \eqref{eq:nyupdate}, it is possible to deduce the following expressions
for the lower and upper bounds of $\yktn$:
\begin{align}
\begin{aligned}
\min_{\PktN} \yktn &=
 \begin{cases}
 %\dfrac{\nktzu \yktzl + s^k_t}{\nktzu + n_k} & \text{if } s^k_t/n_k \ge \yktzl \\
 \big(\nktzu \yktzl + s^k_t\big) / \big(\nktzu + n_k\big) & \text{if } s^k_t/n_k \ge \yktzl \\
 %\dfrac{\nktzl \yktzl + s^k_t}{\nktzl + n_k} & \text{if } s^k_t/n_k <   \yktzl
 \big(\nktzl \yktzl + s^k_t\big) / \big(\nktzl + n_k\big) & \text{if } s^k_t/n_k <   \yktzl
 \end{cases}\,,\\
\max_{\PktN} \yktn &=
 \begin{cases}
 %\dfrac{\nktzu \yktzu + s^k_t}{\nktzu + n_k} & \text{if } s^k_t/n_k \le \yktzu \\
 \big(\nktzu \yktzu + s^k_t\big) / \big(\nktzu + n_k\big) & \text{if } s^k_t/n_k \le \yktzu \\
 %\dfrac{\nktzl \yktzu + s^k_t}{\nktzl + n_k} & \text{if } s^k_t/n_k >   \yktzu
 \big(\nktzl \yktzu + s^k_t\big) / \big(\nktzl + n_k\big) & \text{if } s^k_t/n_k >   \yktzu
 \end{cases}\,.
\end{aligned}
\label{eq:ysetupdate}
\end{align}
The lower bound for $\yktn$ is always attained for $\yktzl$, the upper bound for $\yktzu$.
Note that when $s^k_t/n_k \in [\yktzl, \yktzu]$,
both the lower and the upper bound for $\yktn$ are attained using $\nktzu$,
this corresponds to the spotlight shape.
When $s^k_t/n_k \not\in [\yktzl, \yktzu]$,
due to the banana shape
we will get one of the bounds for $\yktn$ using $\nktzl$.

\begin{figure}
\includegraphics[width=\textwidth]{betaset-binomset1}
\caption{Sets of Beta pdfs (left) and Beta-Binomial cmfs (right, for $m_k=5$)
corresponding to the prior and posterior parameter sets in Figure~\ref{fig:paramsets}.
The sets are depicted as shaded areas,
with the distributions corresponding to the four corners
of the prior parameter set $\PktZ$ (or their posterior counterparts) as solid lines.
The top row depicts the set of prior cdfs/cmfs and the set of posterior cdfs/cmfs for the case where data confirm prior assumptions
(see left panel of Figure~\ref{fig:paramsets});
the bottom row depicts the (identical) set of prior cdfs/cmfs and the set of posterior cdfs/cmfs in case of prior-data conflict
(see right panel of Figure~\ref{fig:paramsets}).
%The set of posteriors and the set of posterior predictive distributions
The set of posterior cdfs and cmfs
is much larger in case of prior-data conflict:
uncertainty due to this conflict is reflected through increased imprecision.}
\label{fig:betaset-binomset}
\end{figure}

The different locations and sizes of $\PktN$ in the conflict versus the no conflict case are then, in turn,
also reflected in the corresponding sets of Beta cdfs and Beta-Binomial cmfs.
As an example, the sets corresponding to the parameter sets in Figure~\ref{fig:paramsets}
are depicted in Figure~\ref{fig:betaset-binomset}.

In the no conflict case (Posterior 1, top row),
the reduction of the $\yktn$ range in $\PktN$ leads to a much smaller set
of Beta and Beta-Binomial distributions.
E.g., the range of predictive probabilities
that two out of a set of five components of type $k$ function at time $t$ 
has changed from $[0.10, 0.28]$ to $[0.11,0.14]$.
This reflects the gain in precision due to test data in accordance with prior assumptions.

In the prior-data conflict case (Posterior 2, bottom row),
the wide $\yktn$ range in $\PktN$ leads to a set of Beta and Beta-Binomial distributions
that is much larger than in the no conflict case.
Here, the range of posterior predictive probabilities
that two out of a set of five components of type $k$ function at time $t$
is now $[0.86, 1.00]$, i.e., less precise than in the no conflict case.
Using sets of Beta priors, the resulting set of posterior predictive Beta-Binomial distributions
adequately reflects the precision of prior information,
the amount of data, and prior-data conflict.

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance in an appropriate way,
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
(It is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
E.g., for any $t < \min(\vec{t}^k)$,
we would get $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
Choosing these limits for $\yktz$ means that we are prepared to give only trivial bounds for the functioning probability,
and do not wish to make any commitments about $p^k_t$ a priori.
Compare this to the uniform prior over $[0,1]$, a usual choice of `noninformative' prior,
being a Beta prior with $\alpha^k_t = \beta^k_t = 1$, i.e., $\nktz = 2$, $\yktz = 0.5$.
Taking this for all $t \in {\cal T}$ means that we expect the component reliability function
to be on average 1/2 for all $t$, a very peculiar assumption,
and, in our view, quite incompatible with the notion of prior ignorance.

%With the bounded domain for $\yktz$ 
%\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
%benavoli zaffalon papers***}
%
%As a note regarding the bounds for $\nktz$,
%for an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
%as then one of the bounds for $\ykt$ is attained for $\nktzl$.
%In a near-noninformative setting, the choice of $\nktzl$ is instead not relevant,
In a near-noninformative setting, the choice of $\nktzl$ is not relevant,
as due to \eqref{eq:ysetupdate}, both lower and upper bound for $\yktn$ are obtained with $\nktzu$; 
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Obviously, one cannot have prior-data conflict in case of prior near ignorance.

@@

We think it is not advisable to express certainty about expected functioning probabilities
with $\nktz$ bounds that vary strongly over $t$.
%***Better to express certainty of prior guess via $\nktz$ bounds?\\
With (strongly) differing $\nktz$ bounds, monotonicty for $\yktn$ bounds cannot be ensured.
%it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so there is no prior-data conflict),
and furthermore no failures happening in $[t_j, t_{j+1}]$, i.e., $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
\begin{itemize}
\item for $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we get $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$, and
\item for $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we get $\ynl_{k,t_j} < \ynl_{k,t_{j+1}}$.
\end{itemize}
Again, this follows from the weighted average property of $\yktn$;
for constant $\yktz$, the lower $\nktz$ the closer $\yktn$ is to $s^k_t/n_k$.
% one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to let them change with $t$ gradually only.

Generally, the interpretation as pseudocount or prior strength should guide the choice of bounds for $\nktz$; 
low values for $\nktz$ as compared to the test sample size $n_k$
give low weight to the prior expected functioning probability intervals $[\yktzl, \yktzu]$,
and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
in a no-conflict situation, when $\nktzu = n_k$ then $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
which means more cautious posterior inferences.
The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
as is clear from Figure~\ref{fig:paramsets} and \eqref{eq:ysetupdate}, the wider the $\nktz$ interval,
the wider $[\yktnl, \yktnu]$ in case of conflict.
So it seems useful to choose $\nktzl = 1$ or $\nktzl = 2$,
while choosing $\nktzu$ with help of the half-width rule as described above.

%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
%to get proper posteriors***
As mentioned in Section~\ref{sec:setsofbetapriors},
it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
this can lead to improper posterior predictive distributions
due to zero arguments for the Beta functions in the denominator of \eqref{eq:LwrSysPost}.
%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
But it is possible to choose values close to $0$ and $1$, respectively,
and due to the linear update step for $\yktn$ (see Eq.~\eqref{eq:nyupdate}),
posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
%***what to do in extreme tail of component distributions?
%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
Likewise, our nonparametric method does not bring unintuitive tail behaviour
as some parametric methods do;
there is no problem in, e.g., assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.

%***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
%as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
While it is possible to set the bounds $\yktzl$ and $\yktzu$ for each $t \in {\cal T}$ individually,
in practice this will be often too time-consuming when ${\cal T}$ forms a dense grid.
%(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Switching to a coarser time grid will waste information from data,
as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
We rather propose to elicit bounds for a subset of ${\cal T}$ only,
and to fill up the time grid with the least committal bounds, i.e.,
taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
and likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
A possible elicitation procedure in this vein could be
to start with eliciting $\yktz$ bounds for a few `central' time points $t$,
filling up the grid as described above accordingly,
and then to further refine the obtained bounds as deemed necessary by the expert.
%`middle' or `typical' $t$,
%then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,
